### 2014-12-10 paper.tex
updated with wasted vote counts, not just seat share

@@

  \section{Discussion}

>>>>

\subsection{Redistricting Processes}
Another key aspect when discussing gerrymandering is the political processes involved in redistricting.  The Constitution provides states with the ability to create their own rules in how districts are drawn, with the provisions that states will ensure balanced district populations, and that districts are redrawn at least every 10 years \cite{LULAC v. Perry, 2006}.\\

Currently, there are five general types of processes, some of which overlap.  The first, and most common, is when redistricting is done by the \textit{legislature}.    The legislature proposes plans and seeks to pass a bill for approval.  Sometimes, this may require a supermajority, or may be veto-proof, but typically requires simple majority approval from both the upper and lower houses and from the governor.  The second is the \textit{advisory commission} model, where a group of people, usually appointed officials, gather together to make non-binding recommendations to the legislature.  The third is the \textit{backup commission}, where failure of the legislature to pass a new plan triggers the activation of a predetermined committee to create an alternative.  The fourth is a \textit{political commission}, where elected officials often serve as members of a redistricting commission.  This is the sole legislative process for districting in New Jersey and Hawaii.  Last, \textit{independent commissions} are appointed groups of unelected officials independent of the legislature, who have full authority for developing new redistricting plans and require bipartisan or non-partisan composition.  This is the sole legislative process for districting in Arizona, Idaho, California, and Washington at the congressional level \cite{Levitt}. \\

In addition to the overlap of legislature control and advisory or backup commissions, there are also some differences between the district drawing process for state legislatures and congressional districts.  For example, Pennsylvania's congressional districts are drawn by the state legislature whereas state legislative districts are drawn by a bipartisan political commission.  Furthermore, many states have different requirements for the composition of commissions, such as some states requiring bipartisan composition, with other states allowing elected officials to serve ex-officio.  Such distinctions create interesting results, as we will see in the Analysis section.

@@

 \subsection{Redistricting Processes}
Taking in the states with at least 10 congressional districts, using both compactness and vote efficiency as a metric for measuring gerrymandering, we also find that purely legislative processes for redistricting produce more  
  \section{Discussion}
